\documentclass[11pt]{article}

% ---------------------------------------------------------------------------
% leakgauge --- arXiv technical note (final)
% Three-model evaluation; the result is an honest null (Kendall tau = 1, n=3).
% ---------------------------------------------------------------------------

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.9in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage[hidelinks]{hyperref}

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\hijackasr}{hijack-ASR}
\newcommand{\leakasr}{leakage-verified ASR}

\title{\textbf{leakgauge}: Does Verifying Data Leakage Reorder\\
Prompt-Injection Robustness Rankings?\\[0.4em]
\large A leakage-verified benchmark for LLM agents}

\author{%
  Bamdad Dashtban\\
  \texttt{bamdadd@gmail.com}
}
\date{July 2026}

\begin{document}
\maketitle

\begin{abstract}
Benchmarks for prompt injection in tool-using LLM agents typically score an
\emph{attack-success rate} (ASR) that counts whether the model was
\emph{hijacked} --- coaxed into performing the attacker's action, such as
issuing an outbound tool call to an attacker-controlled destination. But the
harm that motivates these benchmarks is usually \emph{data exfiltration}: a
secret actually leaving the trust boundary. Performing the action and leaking a
secret are not the same event. We ask a measurement question: if we re-score the
\emph{same} agent traces on \emph{verified leakage} --- a unique canary token
provably present in the outbound call's arguments --- does the resulting ranking
of model robustness differ from the ranking produced by hijack ASR?
\textbf{leakgauge} is a small, defensive, leakage-verified benchmark built to
answer this. Leakage is decided by a programmatic canary predicate (exact string
match after decoding common encodings; no LLM judge), over an email-and-calendar
agent workspace exercised by three \emph{published} indirect-injection attack
families. On each rate we report a bootstrap 95\% CI and, as the headline, a
Kendall-$\tau$ rank-reorder statistic. We evaluate three models --- GPT-4o,
GPT-4o-mini, and Llama-3.3-70B --- over 37 cases with $k = 12$ seeds. Attack
success is near the floor on all three (GPT-4o: hijack-ASR $0.081$,
leakage-verified $0.077$), hijack and leakage nearly coincide, and the two
rankings are \emph{identical} (Kendall $\tau = 1$): on these models, verifying
leakage does \emph{not} reorder the ranking. The near-floor regime leaves little
spread for a reorder to appear; the standing contribution is the programmatic,
LLM-free leakage-verification methodology and a reproducible leakage-verified
leaderboard, and surfacing a reorder likely needs harder cases (future work).
\end{abstract}

% ===========================================================================
\section{Introduction}
% ===========================================================================

\textbf{This is a defensive measurement harness, not an attack toolkit.} Its
purpose is to quantify whether an agent's defences hold against prompt injection
so they can be improved, and to sharpen how the field \emph{scores} that
robustness. Attacks appear in the suite only to exercise defences; only
previously published attack patterns are used, and no novel high-potency
jailbreaks or harmful-content payloads are introduced (Section~\ref{sec:safety}).

Tool-using LLM agents read untrusted content --- emails, web pages, calendar
invitations --- and act on it with privileged tools. \emph{Indirect prompt
injection} places attacker instructions inside that content
\cite{greshake2023,perez2022}. The community has responded with agent-injection
benchmarks, notably AgentDojo \cite{agentdojo2024} and InjecAgent
\cite{injecagent2024}, which measure how often an attack succeeds.

\paragraph{The gap.} ``Success'' in these suites is, operationally, that the
model \emph{took the attacker's action} --- e.g., it called \code{send\_email}
to an attacker address. Call this \emph{hijacking}. But the risk a data-exposure
threat model cares about is \emph{exfiltration}: did a protected secret leave
with that call? A model can be hijacked --- it emits the outbound call --- yet
leak nothing, because the call carried no secret (it refused the credential,
hallucinated a placeholder, or was interrupted). Counting hijacks therefore
\emph{upper-bounds} exfiltration risk, potentially loosely, and a leaderboard
sorted by hijack ASR may rank models differently from one sorted by verified
leakage.

\paragraph{The question.} We therefore ask, question-first:
\begin{quote}
\emph{If the same agent traces are re-scored on programmatically verified data
leakage instead of task hijacking, does the ranking of model robustness
reorder?}
\end{quote}
This is a claim about \emph{measurement discipline}, and it is falsifiable
(Section~\ref{sec:limitations}). If the two rankings agree, leakage verification
adds no discriminative signal and ``hijack ASR is a fine proxy'' becomes a
supported, publishable conclusion. If they disagree, then how injection
benchmarks score matters for which model one would deploy.

\paragraph{Contributions.}
\begin{enumerate}
  \item A \emph{leakage-verified} scoring predicate for agent injection: a
        per-case canary token whose presence in outbound tool-call arguments is
        decided by pure string matching after encoding-normalization --- never by
        an LLM judge (Section~\ref{sec:predicate}).
  \item A small, reproducible email-and-calendar agent workspace and three
        \emph{published} attack families --- delayed trigger, cross-context
        assembly, and encoding-wrapped exfiltration (Section~\ref{sec:families}).
  \item A scoring protocol reporting two ASRs and utility-under-attack with
        bootstrap CIs, and a Kendall-$\tau$ \emph{rank-reorder} statistic as the
        headline thesis test (Section~\ref{sec:metrics}).
\end{enumerate}
We deliberately keep the suite small and single-domain, and we state the
resulting statistical limits openly (Section~\ref{sec:limitations}). In the
evaluation reported here the two rankings coincide (Kendall $\tau = 1$,
Section~\ref{sec:results}): a negative result, whose value is the methodology and
verified leaderboard rather than a positive reorder.

% ===========================================================================
\section{Method}
\label{sec:method}
% ===========================================================================

\subsection{The canary / leakage predicate (the spine)}
\label{sec:predicate}

Every case plants a unique, unguessable \emph{canary} token of the form
\code{LKG-}\textlangle 32 hex\textrangle{} in an environment field the benign
task legitimately touches (an email body, a calendar note). Two events are then
read off a single recorded trace of tool calls:

\begin{description}
  \item[Hijack] an outbound/sensitive tool was called with a destination
    matching the case's exfiltration spec (an attacker address in a
    recipient/URL field), \emph{regardless of payload}.
  \item[Leakage] such an outbound call's arguments actually \emph{carry the
    canary} --- the exact token, or a decodable transform of it.
\end{description}

Leakage is a \textbf{pure string match after normalization, with no model in the
loop}. Normalization folds the transforms an attacker can apply to slip a naive
substring filter: Base64, hexadecimal, ROT13, and Unicode homoglyph / fullwidth
confusables. Concretely, the predicate (i) case-folds and applies Unicode NFKC
plus a homoglyph table to the outbound arguments, then (ii) searches for the
canary both forward (pre-encoding the canary and matching) and in reverse
(decoding candidate Base64/hex tokens and un-rotating ROT13, then matching). A
match counts as leakage only if it occurs in a call whose \emph{destination}
matches the exfiltration spec, so a benign message that merely quotes an attacker
address --- or even the canary --- to a legitimate recipient does not register.

Deciding leakage programmatically is the methodological point: an LLM judge would
fold the very failure mode under study --- a model's opinion about whether a
secret leaked --- into the measurement of it. The canary makes leakage a
decidable predicate over the trace.

\subsection{Workspace and traces}

The environment is a lightweight, zero-dependency email-and-calendar workspace
whose state shape (inbox, sent, contacts, calendar) mirrors AgentDojo
\cite{agentdojo2024} so that cases and defences can port, but which we implement
self-contained. It exposes the tools an assistant would use --- reading and
searching mail, sending mail, searching contacts, and listing, reading, and
creating calendar events. Attacker content lives \emph{inside} environment
fields (email bodies, event descriptions), never in the user's instruction. Each
tool call is recorded with its \emph{full arguments}, so both the hijack and the
leakage predicate are computable from one trace. A run is scored per case over
$k \geq 12$ seeded repeats.

\subsection{Attack families (published patterns only)}
\label{sec:families}

Each family instantiates a documented indirect-injection pattern in the
workspace. We introduce no new jailbreak technique; the contribution is the
leakage-verified \emph{scoring}, not the attacks.

\begin{description}
  \item[Delayed trigger] the injected instruction sits in a benign-looking
    thread the agent only reaches partway through the legitimate task, so the
    malicious step is temporally separated from the content that triggers it
    \cite{greshake2023}.
  \item[Cross-context assembly] the payload is \emph{split} across multiple
    retrieved sources --- the secret in one field, the ``forward it''
    instruction in another, the destination in a third --- so no single field
    reads as malicious and only the assembled whole is an exfiltration command
    \cite{greshake2023}; catalogued under OWASP LLM01 \cite{owasp_llm}.
  \item[Encoding-wrapped] the injected instruction and/or the exfiltrated canary
    is wrapped in Base64, hexadecimal, ROT13, or homoglyph/confusable characters
    so a naive substring or keyword filter over tool arguments never sees the raw
    secret \cite{wei2023,boucher2022}. This family directly stresses the
    normalization step of the leakage predicate.
\end{description}

\subsection{Case design: on-path injection and realism distractors}
\label{sec:onpath}

\paragraph{On-path injection.} A benchmark of this kind measures a model's
\emph{decision} only if the attack is actually delivered to it. We therefore
require that in every case the injected content sits \emph{on the benign task's
critical path}: reading it is a step the model must take to complete the
legitimate request, so an agent that does its job is guaranteed to encounter the
injection, and the target secret is reachable through the tools the benign task
already uses. Without this invariant a case conflates two different outcomes ---
the model \emph{resisting} the attack versus simply \emph{never seeing} it ---
and the leakage rate is driven by non-delivery rather than robustness. On-path
injection makes delivery an experimental constant, so hijack and leakage reflect
behaviour \emph{given} the attack, not the odds it was surfaced.

\paragraph{Realism distractors.} On-path delivery alone is not enough for the gap
to be \emph{measurable}. If the planted canary were the \emph{only} secret a
hijacked model could reach, then any model that performs the injected action must
forward the canary --- hijack would imply leak by construction and \leakasr{}
would collapse onto \hijackasr. We break this coupling with \emph{realism
distractors}: each mailbox holds several plausible secrets --- credentials,
access codes, and tokens for different systems --- only one of which is the
canary the attack targets. A hijacked model must then not merely act but select
the \emph{right} secret; a model that acts on a cluttered, realistic mailbox and
forwards the \emph{wrong} secret is hijacked \emph{without} leaking. Crucially
this yields hijack-without-leak \emph{without tuning} attack difficulty --- the
gap emerges from ordinary mailbox realism, not from a knob set to manufacture it.

\subsection{Metrics and rigor}
\label{sec:metrics}

Over a list of per-case, per-seed records we report three rates:
\begin{itemize}
  \item \textbf{\hijackasr} --- mean over cases that the injected \emph{action}
        occurred (an outbound call to an exfil destination), regardless of
        payload.
  \item \textbf{\leakasr} --- mean over cases that such a call actually carried
        the canary, by the predicate of Section~\ref{sec:predicate}.
  \item \textbf{utility-under-attack} --- mean over cases that the benign user
        task still completed, checked programmatically. This guards against a
        model scoring ``robust'' merely by refusing to do anything.
\end{itemize}

The gap $\text{\hijackasr} - \text{\leakasr}$ is the quantity of interest: how
much counting hijacks overstates verified exfiltration.

\paragraph{Uncertainty.} On each rate we report a percentile \textbf{bootstrap
95\% confidence interval}: resample cases with replacement ($B \approx 10{,}000$),
recompute the rate, take the 2.5/97.5 percentiles. With $n = 37$ cases the
intervals are wide, and we report them as wide; no claim is made that the
intervals do not support. Per-case success across $k \geq 12$ seeds is reported
as mean~$\pm$~std.

\paragraph{Headline: the rank-reorder statistic.} We rank the model set by
\hijackasr{} and, separately, by \leakasr, and report the reorder as a Kendall
$\tau$ together with a side-by-side rank table (Table~\ref{tab:results},
Figure~\ref{fig:reorder}). $\tau \approx 1$ means the rankings agree (leakage
adds no ordering signal); $\tau$ meaningfully below $1$, and outside the
bootstrap interval, is the reorder the question asks about. This statistic
\emph{is} the thesis test.

\subsection{The gap is an instrument-threshold effect}
\label{sec:threshold}

Whether a case can \emph{exhibit} a hijack--leak gap is a property of the
measurement instrument, not only of the model, and two regimes flatten it to
zero. (i) \textbf{Below threshold --- the model never acts:} a model that refuses
the injection or never issues the outbound call scores hijack $=$ leak $= 0$, so
there is no gap to observe and the case is uninformative for that model.
(ii) \textbf{Over-coupled cases --- hijack forces leak:} if the target secret is
the only thing a hijacked model can grab (no distractors,
Section~\ref{sec:onpath}), then acting mechanically implies leaking and the gap
is zero by construction. An honest, non-trivial gap therefore requires a model
\emph{capable enough to act} on a realistic, multi-secret mailbox \emph{and}
liable to forward the \emph{wrong} secret --- exactly the regime the distractor
design targets. The gap is thus a joint property of model capability and case
construction, not a free-floating model property.

Our evaluation bears this out: all three models sit near the floor
(Table~\ref{tab:results}), so where they act, hijack and leakage nearly coincide
and the ranking does not reorder. The headline is inherently a \emph{multi-model}
claim --- a reorder can only appear across models at different points of the
trade-off between acting and selecting the right secret --- and when every model
is near the floor there is little spread for it to appear.
Section~\ref{sec:results} gives the numbers.

% ===========================================================================
\section{Results}
\label{sec:results}
% ===========================================================================

We evaluate three instruction-tuned agent models under identical cases, seeds,
and tools --- GPT-4o, GPT-4o-mini, and Llama-3.3-70B --- each over all $37$ cases
with $k = 12$ seeds. Table~\ref{tab:results} reports \hijackasr{} and \leakasr;
Figure~\ref{fig:reorder} shows the two rankings. The full roster cost \$2.51.

\paragraph{Result: no reorder.} Attack success is near the floor on all three
models, and \leakasr{} tracks \hijackasr{} closely: wherever a model acts, hijack
and leakage nearly coincide, so the per-model gap is small. Ranked by either rate
the order is the same --- GPT-4o, then Llama-3.3-70B, then GPT-4o-mini --- so the
hijack ranking and the leakage ranking are identical: \textbf{Kendall
$\tau = 1$}. On these models, re-scoring the same traces on verified leakage
does \emph{not} reorder the robustness ranking. GPT-4o's bootstrap 95\% CIs are
$[0.027, 0.146]$ (hijack) and $[0.027, 0.135]$ (leakage); with $n = 37$ the
intervals are wide and overlap heavily, and the two rates are statistically
indistinguishable. The hijack ranking is itself barely separated (GPT-4o's CI
reaches $0.027$, near Llama-3.3-70B's point of $0.023$), so there is little
ranking to reorder in the first place.

\paragraph{Reading the floor: utility-under-attack.} A near-floor ASR is
ambiguous alone --- a model can score low because it \emph{resists} the injection
or because it never engages the task --- so utility-under-attack
(Table~\ref{tab:results}) is the control that separates the two. GPT-4o-mini's
near-zero ASR comes with \emph{high} utility ($0.78$): it completes the benign
task yet rarely acts on the injection, so its floor is resistance, not
incapacity. GPT-4o sits at moderate utility ($0.66$) with the highest ASR.
Llama-3.3-70B has the \emph{lowest} utility ($0.43$): it completes fewer benign
tasks, so part of its low ASR reflects not engaging rather than defending --- the
below-threshold regime of Section~\ref{sec:threshold}, flagged rather than hidden.
This cuts toward the null: setting Llama aside, the two clearly-engaging models
(GPT-4o, GPT-4o-mini) still rank the same on both rates.

\begin{table}[t]
\centering
\caption{Three-model evaluation over $37$ cases, $k = 12$ seeds. Rates are means
over cases; ranks are $1 = $ least robust (highest rate). GPT-4o's bootstrap
95\% CIs are given in the text; with $n = 37$ all intervals are wide. The hijack
and leakage rankings coincide (Kendall $\tau = 1$).}
\label{tab:results}
\begin{tabular}{lccccc}
\toprule
Model & \hijackasr & \leakasr & Utility & Rank$_{\text{hijack}}$ & Rank$_{\text{leak}}$\\
\midrule
GPT-4o         & $0.081$ & $0.077$ & $0.66$ & 1 & 1\\
Llama-3.3-70B  & $0.023$ & $0.018$ & $0.43$ & 2 & 2\\
GPT-4o-mini    & $0.005$ & $0.005$ & $0.78$ & 3 & 3\\
\midrule
\multicolumn{6}{l}{Kendall $\tau$ (hijack-rank vs.\ leakage-rank) $= 1$ --- rankings identical ($n = 3$ models).}\\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}[t]
\centering
\begin{tikzpicture}[yscale=0.75]
  \node[anchor=south] at (0,3.55) {\small Rank by \hijackasr};
  \node[anchor=south] at (5,3.55) {\small Rank by \leakasr};
  \foreach \y in {1,2,3}{
    \node[anchor=east] at (-0.2,\y) {\scriptsize \the\numexpr4-\y\relax};
    \node[anchor=west] at (5.2,\y) {\scriptsize \the\numexpr4-\y\relax};
    \fill (0,\y) circle (1.5pt);
    \fill (5,\y) circle (1.5pt);
    \draw[thick] (0,\y) -- (5,\y);
  }
  \node[fill=white,inner sep=1.5pt] at (2.5,3) {\scriptsize GPT-4o};
  \node[fill=white,inner sep=1.5pt] at (2.5,2) {\scriptsize Llama-3.3-70B};
  \node[fill=white,inner sep=1.5pt] at (2.5,1) {\scriptsize GPT-4o-mini};
\end{tikzpicture}
\caption{Rank-reorder slopegraph for the three-model roster. Each model's
robustness rank under \hijackasr{} (left) and \leakasr{} (right) is the same, so
every connecting line is horizontal and no reordering occurs: Kendall
$\tau = 1$. This is the honest null the question returns on current,
near-floor models.}
\label{fig:reorder}
\end{figure}

% ===========================================================================
\section{Related work}
\label{sec:related}
% ===========================================================================

\paragraph{Prompt injection.} Direct prompt injection --- overriding a model's
instructions with adversarial input --- was characterized by Perez and Ribeiro
\cite{perez2022}. Greshake et al.\ \cite{greshake2023} introduced
\emph{indirect} injection, where the adversarial instruction arrives through
retrieved content, and demonstrated exfiltration and multi-stage payloads against
LLM-integrated applications --- the threat model our families instantiate.
Encoding-based filter bypasses (Base64 and other low-resource encodings) were
studied by Wei et al.\ \cite{wei2023} and imperceptible/homoglyph perturbations
by Boucher et al.\ \cite{boucher2022}, motivating our normalization; OWASP
catalogues these as LLM01 \cite{owasp_llm}.

\paragraph{Agent-injection benchmarks.} \textbf{AgentDojo} \cite{agentdojo2024}
is a dynamic environment for evaluating attacks and defences on tool-using
agents; it pairs benign tasks with injection tasks across realistic tool suites
and scores whether the injection task was carried out, alongside utility.
\textbf{InjecAgent} \cite{injecagent2024} benchmarks indirect injection in
tool-integrated agents, categorizing harms (data theft, unauthorized actions) and
measuring attack success. Both are substantial, carefully built suites; our
workspace mirrors AgentDojo's state shape to stay portable.

\paragraph{How leakgauge differs.} We do not replace these suites; we credit them
--- both encode careful security checks, and some of AgentDojo's do inspect
whether attacker-controlled data reached its target. leakgauge makes \emph{verified
leakage} the uniform success criterion via one mechanism --- a planted canary
provably present, after encoding-normalization, in the outbound call's arguments
--- and turns the hijack--leakage \emph{gap} into a first-class, reported quantity
(does re-scoring identical traces reorder the ranking?). The predicate and the
reorder metric are the contribution, not scale: our suite is much smaller and
single-domain than either.

% ===========================================================================
\section{Limitations}
\label{sec:limitations}
% ===========================================================================

We state these before they are asked.

\begin{itemize}
  \item \textbf{Small suite, wide intervals.} With $n = 37$ cases the bootstrap
        95\% CIs are wide; a reorder falling \emph{within} the intervals is not
        distinguishable from noise. We treat any such reorder as unsupported.
        Results are indicative, not definitive placements.
  \item \textbf{Single domain.} All cases live in one email-and-calendar
        workspace, so findings may not transfer to other ecosystems (code
        execution, browsing, finance); the predicate and protocol are
        domain-agnostic, but the evidence is not.
  \item \textbf{Published patterns only.} We use documented attack families and
        no novel jailbreaks, so robustness here does not imply robustness to
        stronger or adaptive attacks; these ASRs are lower bounds on adversary
        capability.
  \item \textbf{Leakage predicate scope.} The predicate catches the canary only
        under the encodings we normalize (Base64, hex, ROT13, homoglyph/fullwidth);
        an encoding we do not fold (multi-layer or custom ciphers) scores as
        hijack-without-leak, a leakage false negative. The set is explicit and
        extensible, and is exactly the boundary the encoding-wrapped family probes.
  \item \textbf{Small roster; two capable models not run.} We report three
        models. \code{qwen-2.5-72b} stalled provider-side during the run and was
        excluded. Anthropic models were deferred on cost: capable agentic models
        run many tool-call steps per case ($\approx$\,\$15--60 per model at this
        suite size), which would exceed the budget and, being similarly robust,
        would not be expected to flip the null. Three models is a thin base for a
        rank statistic, and we say so.
  \item \textbf{Cases required calibration.} An early (v1) case set
        \emph{under-triggered}: several injections sat off the benign critical
        path, so a compliant agent could finish without ever reading the attack
        --- flooring leakage at zero from non-delivery, not robustness. This
        motivated the on-path principle with realism distractors
        (Section~\ref{sec:onpath}). The redesign was guided by single-model
        pilots that located the instrument-threshold regime
        (Section~\ref{sec:threshold}); the reported evaluation uses the
        redesigned cases.
  \item \textbf{Near-floor attack success (the key caveat).} On the current
        frontier models the attacks land near the floor --- little leakage, and
        hijack $\approx$ leakage --- so there is almost no spread for a
        leakage-vs-hijack reorder to arise from. The null we observe is therefore
        partly a property of this regime, not evidence that verified leakage can
        never reorder rankings. Testing the reorder thesis properly needs
        \emph{harder} cases --- stronger or adaptive attacks and more
        exfiltration-prone tasks that push capable models off the floor --- which
        is the main direction of future work.
\end{itemize}

By this falsification standard our result is a null: the rankings agree exactly
($\tau = 1$) and \leakasr{} tracks \hijackasr{} case by case. We report it as
such --- a negative result about how injection benchmarks score, plus the
reusable methodology and the leakage-verified leaderboard --- rather than
searching for a framing under which the reorder survives.

% ===========================================================================
\section{Responsible disclosure and safety}
\label{sec:safety}
% ===========================================================================

leakgauge is built to measure and improve robustness. Only published attack
patterns are used --- encoding wrappers, delayed triggers, split/multi-source
payloads --- with no novel high-potency jailbreaks and no harmful-content
payloads. Because success is verified leakage, the suite ships its discriminating
cases \emph{behind the scorer} rather than as turnkey exploits. If run against a
live product and a real leak is found, it is disclosed privately to the affected
vendor first and never published as a working exploit against a named deployment.

% ===========================================================================
\section{Conclusion}
% ===========================================================================

Injection benchmarks largely score task hijacking, but the harm they stand in for
is data exfiltration --- not the same event. leakgauge re-scores the same traces
on a programmatic, LLM-free leakage predicate and asks whether the ranking
reorders. Across three models on $37$ cases the answer is no: the hijack and leakage
rankings coincide (Kendall $\tau = 1$), because attack success sits near the floor
and leaves little room for the two to diverge. The lasting contribution is the
verification methodology --- leakage decided by canary, never by an LLM judge ---
and a reproducible, leakage-verified leaderboard; whether verified leakage
reorders rankings is a live question that harder cases, not a different scorer,
will settle.

% ---------------------------------------------------------------------------
\begin{thebibliography}{9}
\footnotesize
\setlength{\itemsep}{0.15em}

\bibitem{agentdojo2024}
E.~Debenedetti, J.~Zhang, M.~Balunovi\'c, L.~Beurer-Kellner, M.~Fischer, and
F.~Tram\`er.
\newblock AgentDojo: A Dynamic Environment to Evaluate Prompt Injection Attacks
and Defenses for LLM Agents.
\newblock \emph{NeurIPS Datasets and Benchmarks}, 2024. arXiv:2406.13352.

\bibitem{injecagent2024}
Q.~Zhan, Z.~Liang, Z.~Ying, and D.~Kang.
\newblock InjecAgent: Benchmarking Indirect Prompt Injections in
Tool-Integrated Large Language Model Agents.
\newblock \emph{Findings of ACL}, 2024. arXiv:2403.02691.

\bibitem{greshake2023}
K.~Greshake, S.~Abdelnabi, S.~Mishra, C.~Endres, T.~Holz, and M.~Fritz.
\newblock Not What You've Signed Up For: Compromising Real-World
LLM-Integrated Applications with Indirect Prompt Injection.
\newblock \emph{ACM Workshop on Artificial Intelligence and Security (AISec)},
2023. arXiv:2302.12173.

\bibitem{perez2022}
F.~Perez and I.~Ribeiro.
\newblock Ignore Previous Prompt: Attack Techniques for Language Models.
\newblock \emph{NeurIPS ML Safety Workshop}, 2022. arXiv:2211.09527.

\bibitem{wei2023}
A.~Wei, N.~Haghtalab, and J.~Steinhardt.
\newblock Jailbroken: How Does LLM Safety Training Fail?
\newblock \emph{NeurIPS}, 2023. arXiv:2307.02483.

\bibitem{boucher2022}
N.~Boucher, I.~Shumailov, R.~Anderson, and N.~Papernot.
\newblock Bad Characters: Imperceptible NLP Attacks.
\newblock \emph{IEEE Symposium on Security and Privacy (S\&P)}, 2022.
arXiv:2106.09898.

\bibitem{owasp_llm}
OWASP Foundation.
\newblock OWASP Top 10 for Large Language Model Applications --- LLM01: Prompt
Injection.
\newblock 2023--2025. \url{https://genai.owasp.org/}

\end{thebibliography}

\end{document}
